---
title: "Polling Places Report - {{< meta params.state >}}"
author: "Isabella Velásquez"
date: today
format:
  html:
    theme: [default, custom.scss]
  pdf: default
title-block-banner: images/flag.jpg
execute:
  echo: false
  message: false
  warning: false
params:
  state: "California"
---

In this report, we present a detailed overview of polling places in various counties across the United States, providing information on the total number of polling places and showcasing example locations for each county on election day.[^1]

[^1]: Data from https://github.com/rfordatascience/tidytuesday

```{r}
#| label: setup
library(readr)
library(dplyr)
library(tidyr)
library(tidycensus)
library(tigris)
library(sf)
library(ggplot2)
library(purrr)
library(kableExtra)
polling_places <- read_csv(here::here("data", "geocoded_polling_places.csv"))
```

## `r params$state`

### Overview

:::: {layout-ncol="2"}
::: {}

* Total number of counties: **`r polling_places %>% filter(state == params$state) %>% distinct(county_name) %>% count()`**
* Total number of polling places: **`r polling_places %>% filter(state == params$state) %>% count()`**
* Election Day: **`r polling_places %>% filter(state == params$state) %>% pull(election_date) %>% unique()`**

:::

::: {}

```{r}
#| label: "fig-statemap"
#| fig-cap: "Polling locations in the state"
#| results: hide
us_states <- states(cb = TRUE, resolution = "20m") %>%
  filter(NAME != "Puerto Rico")

ggplot(us_states %>% filter(NAME == params$state)) +
  geom_sf() +
  geom_point(data = polling_places %>% filter(state == params$state),
             aes(x = longitude,
                 y = latitude),
             alpha = 0.4) +
  theme_void() 
```

:::
::::

### POLLING PLACES BY COUNTY

See polling place locations in @fig-statemap.

```{r}
#| results: hide
counties <- polling_places %>% filter(state == params$state) %>% distinct(county_name) %>% pull()
expanded_child <- lapply(counties,
                         function(xx)
                           knitr::knit_expand("_template_params.qmd", current_title = xx))

parsed_child <- knitr::knit_child(text = unlist(expanded_child))
```

`r parsed_child`